Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-04-22 manuscript.Rmd
Updated files.

ggplot(bigList, aes(year, N, group = 1)) + geom_line(colour="#5e3c99") + 
    facet_wrap(~ title, ncol=7) +
    theme_bw() +
    theme(panel.grid.major = element_blank(), 
panel.grid.minor = element_blank(), 
    axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
    scale_x_discrete(breaks=seq(1989, 2020, 8)) + 
    ylim(0, 150)

@@

ggplot(final.list.index, aes(x = scaleScore, y = title)) + geom_point(stat="identity", colour="red") + 
    xlim(c(-3, 3))

@@

>>>>

bigList2 <- left_join(bigList, hIndex, by = "title")
bigList2 <- within(bigList2, quartile <- as.integer(cut(h5Index, quantile(h5Index, probs=0:4/4, na.rm=TRUE), include.lowest=TRUE)))
table(bigList2$h5Index, useNA = "always")

bigList2$quartileFactor <- as.factor(bigList2$quartile)
bigList2 <- bigList2 %>% arrange(desc(quartileFactor))

ggplot(bigList2, aes(year, N, group = 1, colour=quartileFactor)) + geom_line() + 
    facet_wrap(~ shortTitle, ncol=7) +
    theme_bw() +
    theme(panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(), 
    axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
    scale_x_discrete(breaks=seq(1989, 2020, 8)) + 
    ylim(0, 150)

@@

x <- ggplot(final.list.index, aes(x = scaleScore, y = title)) + geom_point(stat="identity", colour="red") + 
    xlim(c(-3, 3))

@@

```{r abstracts}
abstract.df <- filter(full.df, attributes == "abstract")
year.df <- filter(full.df, attributes == "pubYear")
journal.df <- filter(full.df, attributes == "journal")
abstract.df <- left_join(year.df, abstract.df, by = "articleID")
abstract.df <- left_join(abstract.df, journal.df, by = "articleID")
abstract.df <- abstract.df %>% select(-attributes.x, -attributes.y, -attributes)
colnames(abstract.df) <- c("articleID", "year", "abstract", "journal")
abstract.df$abstract <- gsub("[[:punct:]]", "", abstract.df$abstract)
abstract.df$abstract <- tolower(abstract.df$abstract)

ebp.df <- abstract.df[grep("evidence\\s?based\\spractices?|ebp|empirically\\s?supported\\streatments?", abstract.df$abstract), ]
ebp.df$ebp <- rep("ebp", nrow(ebp.df))

meta.df <- abstract.df[grep("meta\\s?analysis", abstract.df$abstract), ]
meta.df$meta <- rep("meta", nrow(meta.df))

rct.df <- abstract.df[grep("randomi[s|z]ed.*trial|[^non]experimental\\sdesign|rct|controlled\\sclinical\\strial|cct", abstract.df$abstract), ]
rct.df$rct <- rep("rct", nrow(rct.df))

systematicReview.df <- abstract.df[grep("systematic\\s?review", abstract.df$abstract), ]
systematicReview.df$systematicReview <- rep("sr", nrow(systematicReview.df))

practiceGuidelines.df <- abstract.df[grep("practice\\sguidelines|treatment\\sguidelines?", abstract.df$abstract), ]
practiceGuidelines.df$practiceGuidelines <- rep("pg", nrow(practiceGuidelines.df))

quasi <- abstract.df[grep("quasi\\s?experimental|non\\s?experimental", abstract.df$abstract), ]
quasi.df$quasi <- rep("quasi", nrow(quasi.df))

longitudinal.df <- abstract.df[grep("longitudinal\\sstudy", abstract.df$abstract), ]
longitudinal.df$longitudinal <- rep("longitudinal", nrow(longitudinal.df))

observational.df <- abstract.df[grep("cohort\\sstudy|case\\scontrol\\sstudy", abstract.df$abstract), ]
observational.df$observational <- rep("observational", nrow(observational.df))

literatureReview.df <- abstract.df[grep("literature\\sreview|review of the.*literature", abstract.df$abstract),]
literatureReview.df$literatureReview <- rep("literatureReview", nrow(literatureReview.df))

survey.df <- abstract.df[grep("survey", abstract.df$abstract), ]
survey.df$survey <- rep("survey", nrow(survey.df))
